Phonon polaritonics in two-dimensional materials

### 2019-01-13 paper.tex
fix v_g in .tex and unicode in .bib

We note that despite its appearance, $\sigma(\omega)$ does not depend on $\epsilon_{\mathrm{env}}$, as $v_g$ has an opposite dependence on $\epsilon_{\mathrm{env}}$. From this relation, it follows that given the properties of the 2D phonons (from experiments or from \emph{ab initio} calculations), one can immediately specify the conductivity. Alternatively, from optical measurements (including far-field measurements) which allow one to extract the conductivity, it becomes possible to extract the group velocity of 2D LO phonons and thus the small-wavevector dispersion of those phonons.

@@

In Figure ~\ref{fig:2}(a), we present the conductivity of 2D hBN of Equation~\ref{eq:localsigma}, using parameters from Ref.~\citenum{sohier2017breakdown} calculated from density functional theory within the local density approximation. In this plot $\epsilon_{\mathrm{env}}=1,$ $\omega_{\mathrm{TO}} = $ \SI{1387}{\per\cm} and $v_g = 1.2\times 10^{-4}c$, with $c$ the speed of light in vacuum.

>>>>

We note that despite its appearance, $\sigma(\omega)$ does not depend on $\epsilon_{\mathrm{env}}$, as $v_{\mathrm{g}}$ has an opposite dependence on $\epsilon_{\mathrm{env}}$. From this relation, it follows that given the properties of the 2D phonons (from experiments or from \emph{ab initio} calculations), one can immediately specify the conductivity. Alternatively, from optical measurements (including far-field measurements) which allow one to extract the conductivity, it becomes possible to extract the group velocity of 2D LO phonons and thus the small-wavevector dispersion of those phonons.

@@

In Figure ~\ref{fig:2}(a), we present the conductivity of 2D hBN of Equation~\ref{eq:localsigma}, using parameters from Ref.~\citenum{sohier2017breakdown} calculated from density functional theory within the local density approximation. In this plot $\epsilon_{\mathrm{env}}=1,$ $\omega_{\mathrm{TO}} = $ \SI{1387}{\per\cm} and $v_{\mathrm{g}} = 1.2\times 10^{-4}c$, with $c$ the speed of light in vacuum.
